---
title: "Japanese plural associative plural on kinship with suffix -tachi"
date: 06.19.2018
author: Kanami Tobe
output:html_document:
    toc: true
    toc_float: true
    code_folding: show

---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Materials  
[Link to the data set](Quantitative-Analysis-and-Visualisation/Project/detasetto.csv) (csv file)  


## Introduction  

"In Japanese there are three plural markers with noun, suffix -tachi, -ra, and -domo.  In CSJ, in comparison with -ra (3,769) and -domo (323), -tachi (6,652) is relatively frequent. Suffix -tachi, which can be attached to most of animate noun, often can be replaced by suffix -ra, which is more formal (Martin 1975). Suffix -domo has depreciative meaning, and often co-occurs with the first person pronoun to express honorific meaning (“humble” first person)." (Tobe,2018)
 
 In the previous reserch, 9 types of vocaburally which cooccuers with plural marker -tachi were found (Human related common noun, Inanimate, Plants, Animal, Kinship, Last Name -san "honorific", Last Name, First name and Pronoun. Often kinship and 

 "The associative plural most likely combines with nouns referring to humans proper names, kinship terms, titles and occupations." (Moravcsik 1994; Corbett 2000: p.102)
But, in Japanese, kinship term often used as a human related common noun. In the privious reserch, it was not mantioned that which kinship term concider to be accociative and additive plural.



## Research hypothesis  

...
There are correlation between type of kinship terms and associative plural.

Null hypothesis on this research is that there will be no correlation between type of kinship terms and associative plural.


## Data  

Original data used in this project was collected from Corpus of Spontaneous Japanese『日本語話し言葉コーパス』. After the collection manually typed data whether the target word set is associative plural or additiveplural by reading sentences. 

Predictor variables: ‘Date’ - numeric; year of the publication ’Genre’ - categorical; 'SPOK' - spoken, 'ACPROSE' - academic prose, 'NONAC' - non-academic prose, 'OTHERPUB' - other publications (includes magazine publications from COCA), 'FICTION', 'NEWS'



```{r dataset}
DS <- read.csv("Quantitative-Analysis-and-Visualisation/Project/detasetto.csv", sep=',',header = TRUE)  
summary(ds)
str(ds)
```

### Data collection and annotation   
Mention the source of your data, details of data collection. Justify the amount of data under study. In addition, you can discuss certain difficulties, peculiarities and shortcomings in data collection and annotation.  
Original data from Corpus of Spontaneous Japanese『日本語話し言葉コーパス』 
190 kinship terms with suffix -tachi found.



### Data considerations

Discuss research design (if applicable), independence, autocorrelation, nestedness of data, possible biases, etc.


## R libraries in use
```{r libraries}
library(tidyverse)
library(DT)
library(psych)
library(ggplot2)
library(tabplot)
# include R libraries here or later
```


## Analysis: descriptive statistics
```

ds <- read.csv("/Users/kanami/Desktop/detasetto.csv", sep=',',header = TRUE)  
sum <- summary(ds)
sum

tableds <- table(ds[,1])
sds <- sort(tableds)



library(DT)
DT::datatable(ds, 
              rownames = FALSE,
              colnames= c("Kinship","Additive or Associative","Transcription", "gender" ),
              caption = "kinship with suffix -tachi")
 
gen <- table(ds[,4])              
pie(gen)
slices <- c(gen) 
lbls <- c("female", "male", "Nutral")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels 
lbls <- paste(lbls,"%",sep="") # ad % to labels 
pie(slices,labels = lbls, col=rainbow(length(lbls)),
  	main="Gender of kinshipterms")

sds[sds>1]

#check the total number of associative and additive
mi<- table(ds$dsds)
mi

#additive 162 and associative 28
barplot(mi, xlab = "Additive D and Associative S", ylab = "number")

#take out only associative plurals
aso <- ds[ds$dsds == "s",]

#gender in associative
asogen <- table(aso$gender)
#kinship in associatives
asokin0 <- table(aso$kinship)
#take a look which kinship terms were used as associatives
asokin <- asokin0[asokin0>0]


```


## Multi-factor analysis  
```
#corrolation 
library(psych)
psych::pairs.panels(ds)

all <- ds[,-3]
pairs(all, panel = panel.smooth)

#take out only additives
adi <- ds[ds$dsds == "d",]

#remove annotation from additives
adic <- adi[,-3]
library(tabplot)
#not good example
tableplot(adic)
#try again with pairs
  pairs(adic, panel = panel.smooth)

#remove annotation from associatives 
asoc <-  aso[,-3]

#check cor in associatives
pairs(asoc, panel = panel.smooth)
```


## Linguistic interpretation of the quantitative results  
No corrolation found which means there are other factors which make kinship term with plural suffix -tachi associative plural.

## Discussion on data distribution and quantitative methods in use   

In conclusion, null hypothesis were accepted. No corrolation found.
used "tabplot" was not a good idea.
