---
title: "Japanese plural asociative plural on kinship with suffix -tachi"
date: 06.19.2018
author: Kanami Tobe
output:html_document:
    toc: true
    toc_float: true
    code_folding: show

---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Materials  
[Link to the data set](Quantitative-Analysis-and-Visualisation/Project/detasetto.csv) (csv file)  


## Introduction  

"In Japanese there are three plural markers with noun, suffix -tachi, -ra, and -domo.  In CSJ, in comparison with -ra (3,769) and -domo (323), -tachi (6,652) is relatively frequent. Suffix -tachi, which can be attached to most of animate noun, often can be replaced by suffix -ra, which is more formal (Martin 1975). Suffix -domo has depreciative meaning, and often co-occurs with the first person pronoun to express honorific meaning (“humble” first person)." (Tobe,2018)
 
 In the previous reserch, 9 types of vocaburally which cooccuers with plural marker -tachi were found (Human related common noun, Inanimate, Plants, Animal, Kinship, Last Name -san "honorific", Last Name, First name and Pronoun. Often kinship and 

 "The associative plural most likely combines with nouns referring to humans proper names, kinship terms, titles and occupations." (Moravcsik 1994; Corbett 2000: p.102)
But, in Japanese, kinship term often used as a human related common noun. In the privious reserch, it was not mantioned that which kinship term concider to be accociative and additive plural.



## Research hypothesis  

...
Discuss possible relevant factors.  
Formulate null hypothesis.


## Data  

* Dependent variable, its type  

* Predictor variables, their types, range/levels  

* Number of observations  

```{r dataset}
DS <- read.csv("/Users/kanami/Desktop/detasetto.csv", sep=',',header = TRUE)  
summary(ds)
str(ds)
```

### Data collection and annotation   
Mention the source of your data, details of data collection. Justify the amount of data under study. In addition, you can discuss certain difficulties, peculiarities and shortcomings in data collection and annotation.  
Original data from Corpus of Spontaneous Japanese『日本語話し言葉コーパス』 
190 kinship terms with suffix -tachi 



### Data considerations

Discuss research design (if applicable), independence, autocorrelation, nestedness of data, possible biases, etc.


## R libraries in use
```{r libraries}
library(tidyverse)
library(DT)
# include R libraries here or later
```


## Analysis: descriptive statistics
```
sum <- summary(ds)
sum

tableds <- table(ds[,1])
ue <- sort(tableds)
DT::datatable(ds, 
              rownames = FALSE,
              colnames= c("Kinship","Additive or Associative","Transcription" ),
              caption = "kinship with suffix -tachi")
             
gen <- table(ds[,4])              
pie(gen)
slices <- c(gen) 
lbls <- c("female", "male", "Nutral")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels 
lbls <- paste(lbls,"%",sep="") # ad % to labels 
pie(slices,labels = lbls, col=rainbow(length(lbls)),
  	main="Gender of kinshipterms")

```

In this section you can put tables and plots that show data distribution for individual variables and distribution for pairs of variables. Histograms, density plots, boxplots (or violin plots), mosaic plots are recommended. You can also provide some basic statistical analysis, such as correlation, statistical significance, t-test and other simple tests. If you calculate a chi-square statistic, do not forget to estimate the effect size.

## Multi-factor analysis  
At least two different methods have to be used. Please provide the output models summaries and graphs. Please evaluate your models (show and interpret relevant indicators such as classification accuracy, goodness of fit, classification power, inertia, variable significance, variable importance, etc.).   
It is recommended to report, when needed, how did you fit the model, did you find any signs of overfitting, why do you believe that certain model is an optimal one, etc.

## Linguistic interpretation of the quantitative results  

## Discussion on data distribution and quantitative methods in use   

In conclusion, you can suggest ideas for further development of your research (correction of hypotheses, work with the data, their statistical analysis).
